---
title: "Data_analyse"
author: "Astrid Elmann"
date: "1/20/2022"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(tidyverse, readbulk, wesanderson, lmerTest, rstatix, ggpubr, plyr, dplyr)
```


```{r, echo=FALSE}
# load data
df <- read_csv("clean_data.csv",
              col_names = TRUE,
              col_types = cols(
                timestamp = col_character() , 
                experiment_ID = col_factor(), 
                subject = col_factor(),
                r_len = col_number(),
                handedness = col_factor(),
                vision = col_factor(),
                colorvision = col_factor(),
                age = col_integer(),
                gender = col_factor(),
                nationality = col_factor(),
                r_type = col_factor(),
                IOS = col_factor(), 
                key_press = col_factor(),
                rt = col_number(),
                trial_stim = col_factor(),
                congruency = col_factor(),
                accuracy = col_factor()
              ))
```

```{r, include=FALSE}
# Make IOS ordered variable (noone chose 2 or 7)
df$IOS <- ordered(df$IOS, levels = c(1, 3, 4, 5, 6))
```

```{r}
glimpse(df)
```


# Se her!!
> Vi laver en standard joint simon task. To personer sidder ved en computer, én skal reagere når den cirkel der dukker op på skærmen er blå, den anden når cirklen er gul. Ved incongruent trials har cirklen været i modsatte side af, hvor forsøgspersonen der skal trykke sidder (Personen sidder f.eks. til højre, og cirklen dukker op i venstre side af skærmen). Congruent trials har cirklen og personen i samme side.
Vi har desuden samlet data om hvor tætte forsøgsdeltagerne føler de er på hinanden. 1 værende ikke særlig tætte, og 7 værende meget tætte.
I alt er der 2 independdent variabler:

 congruency = cirklens position, factor
 
 IOS = Personernes "tæthed", ordinal factor
 
> og én dependent:

  rt = reaktionstid i sekunder, kontunierlig skala
 
> og så skal der self lige huskes at det er et repeated measures design som gør variablen "subject" interessant

```{r, echo=FALSE}
pal <- wes_palettes$FantasticFox1

ggplot(df,(aes( x = IOS, y = rt, fill = congruency))) + 
  geom_boxplot(position=position_dodge(.75)) +
  scale_fill_manual(values = pal) 
```

# -
# Testing hypothesis
# -
# Assumptions for anova

## Condensing to mean
> The mixed effect anova will only take a dataframe with one rt per subject, per congruency, per IOS. Perhaps we're doing something wrong, or should've chosen another model, but to stay in line with the papers we based our experiment on, we want to do an anova.

```{r}
d <- df %>% 
  group_by(subject, congruency, IOS) %>% 
  summarise_at(vars(rt), list(rt = mean)) %>% 
  ungroup()
```

## Outliers

```{r}
d %>% 
  group_by(congruency, IOS) %>%
  identify_outliers(rt)
```

> 1 outlier is found, it is not extreme. Not an issue, we will leave it in. (outliers have been removed in Data_cleaning.Rmd with MAD method)

## Normality
```{r}
# d %>%
#   group_by(congruency, IOS) %>%
#   shapiro_test(rt)

ggqqplot(d, "rt", ggtheme = theme_bw()) +
  facet_grid(IOS ~ congruency, labeller = "label_both")
```
> This test is close to meaningless - we do not have enough data to say anything about normality.

## Homogneity of variance assumption
```{r}
d %>%
  group_by(congruency) %>%
  levene_test(rt ~ IOS)
```
> Somehow, there is homogeneity of variances

## Homogeneity of covariances assumption
```{r}
box_m(d[, "rt", drop = FALSE], d$IOS)
```
> We're good again!

## Assumption of sphericity
> Included in the test

# Mixed anova
```{r}
# Two-way mixed ANOVA test
res.aov <- 
  anova_test(data = d,
  dv = rt, wid = subject,
  between = IOS, within = congruency
  )
get_anova_table(res.aov)
```

# Post hoc
```{r}
d %>%
  pairwise_t_test(
    rt ~ congruency, paired = TRUE, 
    p.adjust.method = "bonferroni"
  )
```


### Numbers for reporting

```{r}
d %>% 
  group_by(congruency) %>% 
  dplyr::summarise(mean = mean(rt), SD = sd(rt))
```

# -
# Difference in relatioinships type
# -
> Literal copy paste of the above, nothing interesting here

```{r, echo=FALSE}
ggplot(df,(aes( x = r_type, y = rt, fill = congruency))) + 
  geom_boxplot(position=position_dodge(.75)) +
  scale_fill_manual(values = pal) 
```

## Condensing to mean

```{r}
d <- df %>% 
  group_by(subject, congruency, r_type) %>% 
  summarise_at(vars(rt), list(rt = mean)) %>% 
  ungroup()
```

## Outliers

```{r}
d %>% 
  group_by(congruency, r_type) %>%
  identify_outliers(rt)
```

> 1 outlier is found, it is not extreme. Not an issue, we will leave it in. (outliers have been removed in Data_cleaning.Rmd with MAD method)

## Normality
```{r}
d %>%
  group_by(congruency, r_type) %>%
  shapiro_test(rt)

ggqqplot(d, "rt", ggtheme = theme_bw()) +
  facet_grid(r_type ~ congruency, labeller = "label_both")
```
> This test is close to meaningless - we do not have enough data to say anything about normality.

## Homogneity of variance assumption
```{r}
d %>%
  group_by(congruency) %>%
  levene_test(rt ~ r_type)
```
> Somehow, there is homogeneity of variances

## Homogeneity of covariances assumption
```{r}
box_m(d[, "rt", drop = FALSE], d$r_type)
```
> We're good again!

## Assumption of sphericity
> Included in the test

# Mixed anova
```{r}
# Two-way mixed ANOVA test
res.aov <- 
  anova_test(data = d,
  dv = rt, wid = subject,
  between = r_type, within = congruency
  )
get_anova_table(res.aov)
```


